Interval Probability for Fuzzy Quantum Theories

### 2016-05-07 prob.tex
prob.tex \subsection{Buffon's Needle Problem} Fix typos, add citation and comments...

Suppose we drop a needle of length $\ell$ onto a floor made of equally
spaced parallel lines a distance $\ell$ apart. It is a known fact that
the probability of the needle crossing a line converges to
$\frac{2}{\pi} = 0.6366197723675814$.
%% \yutsung{Add $\ldots$ at the end? }\\
We analyze this situation in the mathematical framework of probability
spaces paying special attention to the resources needed to estimate
the probability computationally or experimentally.

To formalize the experiment, we consider an experimental setup
consisting of a collection of $N$ identical needles of length
$\ell$. We throw the $N$ needles and observe the number $X$ of needles
that cross a line. The sample space can be expressed as the set
$(X|-)^N$
%% \yutsung{Use more physical or mathematical notation?}\\
of sequences of characters of length $N$ where each character is
either $X$ to indicate a needle crossing a line or $-$ to indicate a
needle not crossing a line. If $N=3$, the event that exactly 2 needles
cross lines is $\{-XX,X-X,XX-\}$: it has
probability~$\frac{2}{3}$. Generally, the event that exactly $M$
needles out of the $N$ total needles cross lines is $\frac{M}{N}$.

In an actual experiment with 500 needles, it was found that 321
crossed a line which gives a probability of $0.642$. In a larger
experiment with $3408$ needles, the probability was calculated to be
$0.6366197193098592$.
%% \yutsung{Add $\ldots$ at the end? }\\
Comparing the values to the idealized mathematical value, we see that
the observed probability approaches $\frac{2}{\pi}$ but only if
\emph{larger and larger resources} are expended.

These resource considerations thus lead us to replace the real
interval $[0,1]$ with rational numbers up to a certain precision.  The
intuition is that the precision depends on the amount of resources
allocated for the measurement process. There is clearly a connection
between the number of needles and the achievable precision: in the
hypothetical experiment with 3 needles, it is not sensible to retain
100 digits in the expansion of $\frac{2}{3}$.

>>>>

Suppose we drop a needle of length $\ell$ onto a floor made of equally
spaced parallel lines a distance $\ell$ apart. It is a known fact that
the probability of the needle crossing a line converges to
$\frac{2}{\pi} = 0.6366197723675814$~\cite{Buffon1777}.
%% \yutsung{Add $\ldots$ at the end? }\\
We analyze this situation in the mathematical framework of probability
spaces paying special attention to the resources needed to estimate
the probability computationally or experimentally.

To formalize the experiment, we consider an experimental setup
consisting of a collection of $N$ identical needles of length
$\ell$. We throw the $N$ needles and observe the number $X$ of needles
that cross a line. The sample space can be expressed as the set
$(X|-)^N$
%% \yutsung{Use more physical or mathematical notation?}\\
of sequences of characters of length $N$ where each character is
either $X$ to indicate a needle crossing a line or $-$ to indicate a
needle not crossing a line. If $N=3$, the event that exactly 2 needles
cross lines is $\{-XX,X-X,XX-\}$: it has
probability~$\frac{3}{8}$. Generally, the event that exactly $M$
needles out of the $N$ total needles cross lines is $\frac{M}{N}$.

In an actual experiment with 500 needles, it was found that 321
crossed a line which gives a probability of $0.642$. In a larger
experiment with $3408$ needles, the probability was calculated to be
$0.6366197193098592$.\\
\yutsung{
May I confirm how many times needle cross the line within $3408$ needles?
Because $\frac{2169}{3408}$ is almost $0.6364436619718310$, and
$\frac{2170}{3408}$ is almost $0.6367370892018779$, both of them are not
close to $0.6366197193098592$ enough\ldots }\\
Comparing the values to the idealized mathematical value, we see that
the observed probability approaches $\frac{2}{\pi}$ but only if
\emph{larger and larger resources} are expended.

These resource considerations thus lead us to replace the real
interval $[0,1]$ with rational numbers up to a certain precision.  The
intuition is that the precision depends on the amount of resources
allocated for the measurement process. There is clearly a connection
between the number of needles and the achievable precision: in the
hypothetical experiment with 3 needles, it is not sensible to retain
100 digits in the expansion of $\frac{2}{\pi}$.
